---
title: "gprofiler_gene_description"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=T)
```


```{r get data}
### Get most diversed gene list
dir_in_res = '../out/20.0216 feat/reg_rf_boruta'
dir_in_anlyz = file.path(dir_in_res, 'anlyz_filtered')
f_featsumm = file.path(dir_in_anlyz,'agg_summary_filtered.csv')
df_aggRes = read.csv(f_featsumm) #aggregated feat summary
div_genes = df_aggRes[,1]
```


```{r g:profiler quest, warning = FALSE}
#install.packages("gprofiler2")
library(gprofiler2)

### g:profiler query for the R result
gostres = gost(query = div_genes, organism = "hsapiens", ordered_query = FALSE,
               multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
                measure_underrepresentation = FALSE, evcodes = TRUE, 
                user_threshold = 0.05, correction_method = "g_SCS", 
                domain_scope = "annotated", custom_bg = NULL, 
                numeric_ns = "", sources = c('GO:BP', 'GO:CC', 'GO:MF'))

# g:profiler query for the R result --generate link and show result on webpage
# gostres = gost(query = div_genes, organism = "hsapiens", ordered_query = FALSE,
#               multi_query = FALSE, significant = TRUE, exclude_iea = FALSE, 
#               measure_underrepresentation = FALSE, evcodes = FALSE, 
#               user_threshold = 0.05, correction_method = "g_SCS", 
#               domain_scope = "annotated", custom_bg = NULL, 
#               numeric_ns = "", sources = NULL,as_short_link = TRUE)

# Save gostres result
write.csv(apply(gostres$result,2,as.character),'target_gores.csv',row.names = FALSE)
```

Interactive plot showing gene description
```{r gprofiler Manhattan plot}
### visulization capped interaction plot (p>16)
# p.capped = gostplot(gostres, capped =TRUE, interactive = T)
### visulization uncapped interaction plot
p.uncapped = gostplot(gostres, capped = FALSE, interactive = T)
p.uncapped
```


4 out of top5 GO:BP terms are related to cell cycle. These genes include cyclinD gene, cyclin-dependent kinase gene and cell cycle check point.
```{r TOP5 GO:BP term table, warning=FALSE, error=FALSE}
### Get GO:BP dataframe
p = gostplot(gostres, capped =FALSE, interactive = F)
# saving plot
# publish_gostplot(p,height = 10, width = 15, filename = 'gene_desp_gprofiler.png')
gostres.sig = gostres$result[gostres$result$p_value<5e-2,]
gostres.sig = gostres.sig[order(gostres.sig$p_value),]

res.gobp = gostres.sig[grep('GO:BP',gostres.sig$source),]
res.gocc = gostres.sig[grep('GO:CC',gostres.sig$source),]
res.gomf = gostres.sig[grep('GO:MF',gostres.sig$source),]




### Show data frame -- intersection shows the genes under that term
# cc.genes = res.gobp$intersection[1:5]

### Table only
# publish_gosttable(gostres, res.gobp[c(1:5),],use_colors = T,
#                  show_columns = c("source", "term_id", "term_name","term_size","intersection_size"),filename = NULL)

# Top5 plot and table
# for display
p.gobp = publish_gostplot(p, res.gobp[c(1:5),],filename = NULL)
# for saving
# p.gobp = publish_gostplot(p, res.gobp[c(1:5),], width = 15, height = 10, filename = 'cellcycle_gprofiler.png')
```


Mitochondrial terms
```{r Mitochondrial term table, warning=FALSE, error=FALSE}
### Get mitocondria dataframe
res.mito = gostres$result[grep('^mitochon',gostres$result$term_name),]
res.mito = res.mito[order(res.mito$p_value), ]
row.names(res.mito) = NULL

### Table only
# publish_gosttable(gostres, res.gobp,use_colors = T,
#                  show_columns = c("source", "term_id", "term_name","term_size","intersection_size"),filename = NULL)

# Plot with emphasized dot and table
# for display
p.mito = publish_gostplot(p, res.mito,width = 15, height = 10, filename = NULL)
# for saving file
# p.mito = publish_gostplot(p, res.mito,width = 15, height = 10, filename = 'mito_gprofiler.png')
```

Some top terms are under GO:CC(cellular component). List top significant terms. 
However, most of the top terms have large term size, so it's not surprising that most genes are mapped.
```{r TOP10 GO:CC term table, warning=FALSE}
### Get GO:CC dataframe
res.gocc = gostres$result[grep('GO:CC',gostres$result$source),]

### GO:CC result table only- TOP15
# tab.gocc = publish_gosttable(gostres, res.gocc[c(1:15),],use_colors = T,
 #                 show_columns = c("source", "term_id", "term_name","term_size","intersection_size"),filename = NULL)

### GO:CC nucleous related 
# Get dataframe
res.gocc.nuc = res.gocc[grep('nuc', res.gocc$term_name),]
# table only
# publish_gosttable(gostres, res.gocc.nuc ,use_colors = T,
#                  show_columns = c("source", "term_id", "term_name","term_size","intersection_size"),filename = NULL)
# plot and table
p.gocc.nuc = publish_gostplot(p, res.gocc.nuc,filename = NULL)


### GO:CC lumen related 
#get dataframe
res.gocc.lum = res.gocc[grep('lumen', res.gocc$term_name),]
# table only
# publish_gosttable(gostres, res.gocc.lum ,use_colors = T,
#                  show_columns = c("source", "term_id", "term_name","term_size","intersection_size"),filename = NULL)
# plot and table
p.gocc.lum = publish_gostplot(p, res.gocc.lum,filename = NULL)

```


Catalytic function related terms are also enriched
```{r}
p.cat = publish_gostplot(p, highlight_terms = c("GO:0032991","GO:0003824","GO:1902494"),filename = NULL)
```


miRNA that associate with cancer is highly significant
```{r}
p.mirna=publish_gostplot(p, highlight_terms = c("MIRNA:hsa-miR-16-5p"),filename = NULL)
```
```{r  all top 20 term table, warning=FALSE, echo=F}
# p = gostplot(gostres, capped =TRUE, interactive = F)
# order by pvalue
# res.pvalord = gostres$result[order(gostres$result$p_value),]

# Top5 plot and table
# publish_gostplot(p, res.pvalord[c(1:10),],
#                 filename = NULL)
# Table only
# publish_gosttable(gostres, res.pvalord[c(1:10),],
#                  use_colors = T,
#                  show_columns = c("source", "term_id", "term_name","term_size","intersection_size"),
#                  filename = NULL)
```



```{r gprofiler reproducibility}
# get g:profiler version --Please use "set_base_url" and switch to this version for later users
gostres$meta$version
```